### 2015-11-13 postdoctoral/gamma_functions.tex
abstracted inverse limits with uncountable indices are trivial or nonmetrizable

@@

@@

    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
    is of the form
    \([U,F]\) where \(U(l)\) is an open interval in \(M\) for each
    \(l\in F\in [L]^{<\omega}\), and
    \([U,F]=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
    If we assume that \([U,F]\) is non-empty, one of the following
    must hold:

    \begin{itemize}
      \item
        \(U[l_0]=(a,b)\) for some \(l_0\in F\).
        Then \([U,F]=[U,\{l_0\}]\), and note that
        \(
          [U,\{l_0\}]
            =
          (\vect x_{(\leftarrow,l_0],a},\vect x_{(\leftarrow,l_0],b})
        \).
      \item
        \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
        and \([U,F]=[U,\{l_0,l_1\}]\). Then
        \([U,\{l_0,l_1\}]=(\vect x_{l_0,a},\vect x_{l_1,b})\).
    \end{itemize}
    In the other direction, consider \(\vect y\in(\vect x,\vect z)\).
    \begin{itemize}
      \item
        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\)
        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\), let
        \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
      \item
        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\),
        \(\rho(\vect y)=\rho(\vect z)\), and \(v(\vect y)<v(\vect z)\),
        it follows that \(\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_1]\),
        so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
      \item
        In the case that
        \(\rho(\vect x)=\rho(\vect y)\), \(v(\vect x)<v(\vect y)\),
        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\),
        it follows that \(\rho(\vect x)=\rho(\vect y)=(\leftarrow,l_0]\),
        so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
      \item
        In the case that
        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)\) and
        \(v(\vect x)<v(\vect y)<v(\vect z)\),
        it follows that
        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_0]\),
        so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
        \(\vect y\in[U,\{l_0\}]=(\vect x,\vect z)\).
    \end{itemize}

@@

    We claim that the bijection \(\theta(\vect x_{C,m})=\<C,m\>\) is a
    homeomorphism. Note that basic open sets of
    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).

@@

    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
    \(\vect x_{C,m}\in[U,\{l_0\}]\).
    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
    in particular, it's nonzero. So
    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    In the case that \(V=(A,B)\), we may also choose \(l_1\in B\setminus C\).
    We again let \(U(l_0)=W\), and we also let \(U(l_1)=Z\). Then as
    \(\vect x_{C,m}(l_0)=m\in W=U(l_0)\) and
    \(\vect x_{C,m}(l_1)=0\in Z=U(l_1)\), we have shown
    \(\vect x_{C,m}\in[U,\{l_0,l_1\}]\). For any \(\vect x_{D,n}\in[U,\{l_0,l_1\}]\),
    \(\vect x_{D,n}(l_0)\in W\) and \(\vect x_{D,n}(l_1)\in Z\).
    This shows that \(\vect x_{D,n}(l_0)=n\in W\) and \(\vect x_{D,n}(l_1)=0\), so
    \(
      A
        \subsetneq
      (\leftarrow,l_0]
        \subseteq
      D
        \subsetneq
      (\leftarrow,l_1]
        \subseteq
      B
    \), putting \(D\in(A,B)=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
    open set \([U,F]\) of
    \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\).
    It follows that \(m\in U(l)\) for all \(l\in F\cap C\),
    and \(0\in U(l)\) for all \(l\in F\setminus C\).

    If \(F\subseteq C\), then let \(l_0\) be the maximum element of \(F\) and
    \(U'=\bigcap_{l\in F}U(l)\). Note \(\<C,m\>\in((\leftarrow,l_0),L]\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),L]\times U'\). Since \(l_0\in D\),
    \(\vect x_{D,n}(l_0)=n\in U'\). Since \(n\not=0\), we have
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\), so
    \(\vect x_{D,n}\in[U,F]\).

    If \(F\cap C=\emptyset\), then
    let \(l_1\) be the minimum element of \(F\setminus C\).
    Note \(\<C,m\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    So let \(\<D,n\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    Since \(l_1\not\in D\), \(\vect x_{D,n}(l)=0\in U(l)\) for all \(l\in F\),
    giving \(\vect x_{D,n}\in[U,F]\).

    Otherwise, let \(l_0\) be the maximum element of \(F\cap C\) and
    \(l_1\) be the minimum element of \(F\setminus C\).
    Let \(U'\subseteq \bigcap_{l\in C\cap F}U(l)\) and
    \(U''\subseteq \bigcap_{l\in F\setminus C}U(l)\).
    Note \(\<C,m\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    Since \(l_0\in D\) and \(l_1\not\in D\), we have
    \(\vect x_{D,n}(l_0)=n\in U'\) and
    \(\vect x_{D,n}(l_1)=0\in U''\). Furthermore,
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\cap C\), and
    \(\vect x_{D,n}(l)=0\in U''\subseteq U(l)\) for all \(l\in F\setminus C\),
    so \(\vect x_{D,n}\in[U,F]\).
  \end{proof}

@@

    Consider the basic open neighborhood \([U,F]\) of \(\vect 0\) in
    \(\varprojlim\{M,\nu,L\}\). Let \(l_1\) be the least element of \(F\),
    and \(U'=\bigcap_{l\in F}U(l)\). Note that
    \(
      \{\emptyset\}\times M\cup\check L\times \{0\}
        \subseteq
      [\emptyset,(\leftarrow,l_1])\times M
      \cup
      \check L\times U'
    \). So let
    \(
      \vect x_{C,m}
        \in
      [\emptyset,(\leftarrow,l_1])\times M
    \),
    and note that as \(l_1\not\in C\), \(\vect x_{C,m}(l)=0\in U(l)\) for all
    \(l\in F\), and thus \(\vect x_{C,m}\in[U,F]\).
    Likewise if we let
    \(
      \vect x_{C,m}
        \subseteq
      \check L\times U'
    \),
    we have that \(x_{C,m}(l)\in U'\subseteq U(l)\) for all \(l\in L\), and
    thus \(\vect x_{C,m}\in[U,F]\).

    Now in \((\check L\times M)/\sim\)
    consider the basic open set formed by the union of
    \(V\times M\) containing \(\{\emptyset\}\times M\) and
    \(\check L\times W\) containing \(\check L\times \{0\}\).
    \(V=[\emptyset,B)\) for some nonempty leftward set \(B\),
    so choose \(l_0\in B\) and note that as
    \((\leftarrow,l_0]\subseteq B\) we have
    \([\emptyset,(\leftarrow,l_0])\subseteq[\emptyset,B)=V\).
    So let \(U(l_0)=W\) and note \(\vect 0\in[U,\{l_0\}]\). For any
    \(\vect x_{C,m}\in[U,\{l_0\}]\), we have two cases.

>>>>

\usepackage{stmaryrd}

\newcommand{\lb}{\llbracket}
\newcommand{\rb}{\rrbracket}

@@

  \begin{theorem}
    \(\check L\) is metrizable if and only if \(L\) is countable.
  \end{theorem}

  \begin{proof}
    If \(L\) is uncountable, let \(\mc B\) be a base for \(\check L\).
    For each \(l\in L\), there is some neighborhood \(B_l\in\mc B\) of
    \((\leftarrow,l)\) which is a subset of
    \([\emptyset,(\leftarrow,l])=[\emptyset,(\leftarrow,l)]\). Each \(B_l\)
    is unique, so \(\check L\) is compact but not second countable,
    and therefore nonmetrizable.

    If \(L\) is countable, then note that the union of
    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
    generates a countable base for \(\check L\). Thus \(\check L\) is
    compact second-countable, and therefore metrizable.
  \end{proof}

@@

    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
    is of the form
    \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
    \(l\in F\in [L]^{<\omega}\), and
    \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
    If we assume that \(\lb U,F \rb\) is non-empty, one of the following
    must hold:

    \begin{itemize}
      \item
        \(U[l_0]=(a,b)\) for some \(l_0\in F\).
        Then \(\lb U,F\rb=\lb U,\{l_0\}\rb \), and note that
        \(
          \lb U,\{l_0\}\rb
            =
          (\vect x_{(\leftarrow,l_0],a},\vect x_{(\leftarrow,l_0],b})
        \).
      \item
        \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
        and \(\lb U,F\rb=\lb U,\{l_0,l_1\}\rb \). Then
        \(\lb U,\{l_0,l_1\}\rb =(\vect x_{l_0,a},\vect x_{l_1,b})\).
    \end{itemize}
    In the other direction, consider \(\vect y\in(\vect x,\vect z)\).
    \begin{itemize}
      \item
        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\)
        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\), let
        \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
      \item
        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\),
        \(\rho(\vect y)=\rho(\vect z)\), and \(v(\vect y)<v(\vect z)\),
        it follows that \(\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_1]\),
        so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
      \item
        In the case that
        \(\rho(\vect x)=\rho(\vect y)\), \(v(\vect x)<v(\vect y)\),
        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\),
        it follows that \(\rho(\vect x)=\rho(\vect y)=(\leftarrow,l_0]\),
        so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
      \item
        In the case that
        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)\) and
        \(v(\vect x)<v(\vect y)<v(\vect z)\),
        it follows that
        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_0]\),
        so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
        \(\vect y\in\lb U,\{l_0\}\rb =(\vect x,\vect z)\).
    \end{itemize}

@@

    We claim that the bijection \(\theta(\vect x_{C,m})=\<C,m\>\) is a
    homeomorphism. Note that basic open sets of
    \(\varprojlim\{M,\nu,L\}\) are of the form \(\lb U,F \rb\) where \(U(l)\) is
    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).

@@

    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
    \(\vect x_{C,m}\in\lb U,\{l_0\}\rb \).
    For any \(\vect x_{D,n}\in\lb U,\{l_0\}\rb \) we have that \(\vect x_{D,n}(l_0)=n\in W\);
    in particular, it's nonzero. So
    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    In the case that \(V=(A,B)\), we may also choose \(l_1\in B\setminus C\).
    We again let \(U(l_0)=W\), and we also let \(U(l_1)=Z\). Then as
    \(\vect x_{C,m}(l_0)=m\in W=U(l_0)\) and
    \(\vect x_{C,m}(l_1)=0\in Z=U(l_1)\), we have shown
    \(\vect x_{C,m}\in\lb U,\{l_0,l_1\}\rb \). For any \(\vect x_{D,n}\in\lb U,\{l_0,l_1\}\rb \),
    \(\vect x_{D,n}(l_0)\in W\) and \(\vect x_{D,n}(l_1)\in Z\).
    This shows that \(\vect x_{D,n}(l_0)=n\in W\) and \(\vect x_{D,n}(l_1)=0\), so
    \(
      A
        \subsetneq
      (\leftarrow,l_0]
        \subseteq
      D
        \subsetneq
      (\leftarrow,l_1]
        \subseteq
      B
    \), putting \(D\in(A,B)=V\). Thus
    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).

    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
    open set \(\lb U,F \rb\) of
    \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\).
    It follows that \(m\in U(l)\) for all \(l\in F\cap C\),
    and \(0\in U(l)\) for all \(l\in F\setminus C\).

    If \(F\subseteq C\), then let \(l_0\) be the maximum element of \(F\) and
    \(U'=\bigcap_{l\in F}U(l)\). Note \(\<C,m\>\in((\leftarrow,l_0),L]\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),L]\times U'\). Since \(l_0\in D\),
    \(\vect x_{D,n}(l_0)=n\in U'\). Since \(n\not=0\), we have
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\), so
    \(\vect x_{D,n}\in\lb U,F\rb\).

    If \(F\cap C=\emptyset\), then
    let \(l_1\) be the minimum element of \(F\setminus C\).
    Note \(\<C,m\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    So let \(\<D,n\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
    Since \(l_1\not\in D\), \(\vect x_{D,n}(l)=0\in U(l)\) for all \(l\in F\),
    giving \(\vect x_{D,n}\in\lb U,F\rb\).

    Otherwise, let \(l_0\) be the maximum element of \(F\cap C\) and
    \(l_1\) be the minimum element of \(F\setminus C\).
    Let \(U'\subseteq \bigcap_{l\in C\cap F}U(l)\) and
    \(U''\subseteq \bigcap_{l\in F\setminus C}U(l)\).
    Note \(\<C,m\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    So let \(\<D,n\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
    Since \(l_0\in D\) and \(l_1\not\in D\), we have
    \(\vect x_{D,n}(l_0)=n\in U'\) and
    \(\vect x_{D,n}(l_1)=0\in U''\). Furthermore,
    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\cap C\), and
    \(\vect x_{D,n}(l)=0\in U''\subseteq U(l)\) for all \(l\in F\setminus C\),
    so \(\vect x_{D,n}\in\lb U,F\rb\).
  \end{proof}

@@

    Consider the basic open neighborhood \(\lb U,F]\) of \(\vect 0\) in
    \(\varprojlim\{M,\nu,L\}\). Let \(l_1\) be the least element of \(F\),
    and \(U'=\bigcap_{l\in F}U(l)\). Note that
    \(
      \{\emptyset\}\times M\cup\check L\times \{0\}
        \subseteq
      [\emptyset,(\leftarrow,l_1])\times M
      \cup
      \check L\times U'
    \). So let
    \(
      \vect x_{C,m}
        \in
      [\emptyset,(\leftarrow,l_1])\times M
    \),
    and note that as \(l_1\not\in C\), \(\vect x_{C,m}(l)=0\in U(l)\) for all
    \(l\in F\), and thus \(\vect x_{C,m}\in\lb U,F\rb\).
    Likewise if we let
    \(
      \vect x_{C,m}
        \subseteq
      \check L\times U'
    \),
    we have that \(x_{C,m}(l)\in U'\subseteq U(l)\) for all \(l\in L\), and
    thus \(\vect x_{C,m}\in\lb U,F\rb\).

    Now in \((\check L\times M)/\sim\)
    consider the basic open set formed by the union of
    \(V\times M\) containing \(\{\emptyset\}\times M\) and
    \(\check L\times W\) containing \(\check L\times \{0\}\).
    \(V=[\emptyset,B)\) for some nonempty leftward set \(B\),
    so choose \(l_0\in B\) and note that as
    \((\leftarrow,l_0]\subseteq B\) we have
    \([\emptyset,(\leftarrow,l_0])\subseteq[\emptyset,B)=V\).
    So let \(U(l_0)=W\) and note \(\vect 0\in\lb U,\{l_0\}\rb \). For any
    \(\vect x_{C,m}\in\lb U,\{l_0\}\rb \), we have two cases.
